Interactive Filter and Display of Hillary Clinton's Emails: \\A Cautionary Tale of Metadata

### 2017-03-25 VAST_submission/vgtc_journal_latex/paper.tex
Paper update
More paper writing

@@

>>>>

Unfortunately, this data is not perfect. The PDF files released by the state department do not include the typical email server header with information about the time stamp inforamtion, the addresses of all involved, and other useful and regular information. Instead, these files appear more similar to screen captures of the emails, providing only the visual display a user would see without the useful information used to generate that display. As a result, the email addresses are occasionally not included, and there were initially concerns over the time zones used to generate the time stamp metadata. Furthermore, the HTML data on Wikileaks is frequently irregular in form, and although work has been done to make the cleaning and extraction functions as general as possible, there are still certainly fringe cases not considered which occur frequently enough to have an impact. It is also important to keep in mind the fact that the data have already been filtered twice. First by the emails chosen to be released by Clinton, and next by the emails and email sections which the State Department chose not to redact. Indeed, even the metadata can be affected by this redaction, as a number of individuals have their email addresses redacted in all communications, preventing certain analysis from being performed.

@@

The app (HOST ADDRESS) provides the ability for users to place custom filters on the time frame of server time stamps and classification tags of the emails and view how a series of three displays change. The first of these is a spoked network graph of all corresponents with Clinton at the centre. The spokes are separated into two groups by the radial length of the spokes, these groups are determined automatically by the largest difference in volume of correspondence present in the data between the ordered counts of number of emails sent between individuals. As well, the width of the edges of the graph is determined by the volume of correspondence which occurred between Clinton and the correspondent in either direction. Finally, all edges and points are coloured according to a simple scheme. If the name associated with a node in the graph is at any point associated with an email address hosted at some '.gov' domain in the correspondences, they are coloured blue. Individuals with email addresses which are identifiably not hosted at a '.gov' domain are coloured red. Finally, individuals which cannot have their email host domain identified are coloured grey. It is important to note that for those individuals with grey spokes, the reason the email is not identifiable is the removal of the email by the state department. Such a redaction is not a guarantee that the email said individual used is not an official state email, but it is an indication that the email address is viewed as personal or private information, which suggests some email hosted outside of the '.gov' domain.
